---
author: Manjunath Mallikarjun Kendhuli
title: Student
format:
  classic-cv-pdf: default
cvfooter:
  left: "mr.schochastics.net"
  right: "github.com/manjumk3108"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Student in HS Fresenius
    right: Cologne, Germany
  - title: Field
    left: International Business and Management
    right: http://linkedin.com/in/manjunath-m-kendhuli-399530217
  - title: Techs
    left: R, Python, javascript, SQL
    right: manjukendhuli@gmail.com
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

Master’s student in Industrial Engineering and International Management with nearly two years of experience as a Technical Consultant. Skilled in database management, system optimization, and implementation projects. Demonstrated expertise in cross-functional collaboration and data-driven problem-solving. Strong analytical, problem-solving, and leadership abilities, aspiring to transition into management roles like Business Data Analysis, Consulting, and Project Management.

# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Assistant System Engineer", "TCS Bengluru, India", "Sep. 2022 - Jun. 2024",
    "Transparent Social Analytics, Department of Computational Social Science", c("Interacted with clients to gather and analyze requirements, ensuring effective communication and alignment with business needs", "Applied problem-solving techniques to complex tasks, showcasing adaptability and critical thinking in project delivery"),
    
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Master's of Science", "Fresenius University of Applied Sciences", "Cologne, Germany", "Aug. 2024 - Sep. 2026", c("Thesis: Project Management in Agile Projects", "Data Analysis Replication")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
